DeepSphere: a graph-based spherical CNN

### 2019-11-13 main.tex
update a bit the appendix

\paragraph{Preliminaries.}
The proof of theorem \ref{theo:pointwise convergence for a regular sampling} is inspired from the work of \cite{belkin2005towards}. As a result, we start by restating some of their results.
Given a sampling $\V = \{x_i\in\mathcal M\}_{i=0}^{n-1}$ of a closed, compact and infinitely differentiable manifold $\mathcal{M}$, a smooth ($\in\mathcal{C}_\infty(\mathcal{M)}$) function  $f:\mathcal{M} \rightarrow \mathbb{R}$, and defined the vector $\b{f}$ of samples of $f$ as follows: $T_\V f = \b{f} \in \mathbb{R}^n,\ \b{f}_i = f(x_i)$.
The proof is constructed by leveraging 3 different operators:
\begin{itemize}
    \item The extended graph Laplacian operator \eqref{eq:Heat Kernel Graph Laplacian operator}
	\item The functional approximation to the Laplace-Beltrami operator is a linear operator $L^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ defined  as
	\begin{equation}
    \label{eq:Functional approximation to the Laplace-Beltrami operator}
	L^tf(y) = \int_{\mathcal{M}} e^{-\frac{\|x-y\|^2}{4t}}\left(f(y)-f(x)\right)d\mu(x),
	\end{equation}
	where $\mu$ is the uniform probability measure on the manifold $\mathcal{M}$, and $\text{vol}(\mathcal{M})$ is the volume of $\mathcal{M}$.
	\item
	The Laplace-Beltrami operator $\Delta_{\mathcal{M}}$ is defined as the divergence of the gradient
	\begin{equation}
        \label{eq:laplace-beltrami}
        \Delta_{\mathcal M}f(y):= -\text{div}(\nabla_{\mathcal M}f)
    \end{equation}
    of a differentiable function $f: \mathcal M\rightarrow \R$. The gradient $\nabla f: \mathcal M \rightarrow T_p\mathcal M$ is a vector field defined on the manifold pointing towards the direction of steepest ascent of $f$, where $T_p\mathcal M$ is the affine space of all vectors tangent to $\mathcal M$ at $p$.

>>>>

\paragraph{Preliminaries.}
The proof of theorem \ref{theo:pointwise convergence for a regular sampling} is inspired from the work of \cite{belkin2005towards}. As a result, we start by restating some of their results.
Given a sampling $\V = \{x_i\in\mathcal M\}_{i=0}^{n-1}$ of a closed, compact and infinitely differentiable manifold $\mathcal{M}$, a smooth ($\in\mathcal{C}_\infty(\mathcal{M)}$) function  $f:\mathcal{M} \rightarrow \mathbb{R}$, and defined the vector $\b{f}$ of samples of $f$ as follows: $T_\V f = \b{f} \in \mathbb{R}^n,\ \b{f}_i = f(x_i)$.
The proof is constructed by leveraging 3 different operators:
\begin{itemize}
  \item As a reminder of \eqref{eq:Heat Kernel Graph Laplacian operator}, the extended graph Laplacian operator is a linear operator $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$  is defined as
	\begin{equation}
	\label{eq:Heat Kernel Graph Laplacian operator}
	 L_n^tf(y) := \frac{1}{n}\sum_{i=0}^{n-1} e^{ -\frac{\|x_i-y\|^2}{4t}} \left(f(y)-f(x_i)\right).
	\end{equation}
	Note that we have the following relation $\b{L}_n^t \b{f} = T_\V L_n^t f$.
	\item The functional approximation to the Laplace-Beltrami operator is a linear operator $L^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ defined  as
	\begin{equation}
    \label{eq:Functional approximation to the Laplace-Beltrami operator}
	L^tf(y) = \int_{\mathcal{M}} e^{-\frac{\|x-y\|^2}{4t}}\left(f(y)-f(x)\right)d\mu(x),
	\end{equation}
	where $\mu$ is the uniform probability measure on the manifold $\mathcal{M}$, and $\text{vol}(\mathcal{M})$ is the volume of $\mathcal{M}$.
	\item
	The Laplace-Beltrami operator $\Delta_{\mathcal{M}}$ is defined as the divergence of the gradient
	\begin{equation}
        \label{eq:laplace-beltrami}
        \Delta_{\mathcal M}f(y):= -\text{div}(\nabla_{\mathcal M}f)
    \end{equation}
    of a differentiable function $f: \mathcal M\rightarrow \R$. The gradient $\nabla f: \mathcal M \rightarrow T_p\mathcal M$ is a vector field defined on the manifold pointing towards the direction of steepest ascent of $f$, where $T_p\mathcal M$ is the affine space of all vectors tangent to $\mathcal M$ at $p$.
